Patient movements

### 2024-11-19 analysis/environmental-data.Rmd
CO2 and occupancy time series plots

```{r}
co2_pl <- cont_df %>%
  mutate(time = floor_date(time, "10 minutes")) %>%
  group_by(mthdy, time, room) %>%
  summarize(co2 = mean(co2)) %>%
  ungroup() %>%
  mutate(room = factor(
    room,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = time, y = co2, color = mthdy)) +
  geom_step() +
  facet_wrap(~room) +
  coord_cartesian(expand = FALSE) +
  scale_x_datetime(date_breaks = "4 hours", date_labels = "%H:%M") +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(
    y = expression("CO"[2] * " (parts per million, ppm)")
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.key.width = unit(0.275, "cm"),
    legend.key.height = unit(0.2, "cm")
  )

save_plot(
  co2_pl,
  pdf_file = "results/data/co2-levels-over-time.png",
  w = 16, h = 10
)
```

>>>>

```{r}
co2_pl <- cont_df %>%
  mutate(time = floor_date(time, "10 minutes")) %>%
  group_by(mthdy, time, room) %>%
  summarize(co2 = mean(co2)) %>%
  ungroup() %>%
  mutate(room = factor(
    room,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = time, y = co2, color = mthdy)) +
  geom_step() +
  facet_wrap(~room, ncol = 1) +
  scale_y_continuous(
    limits = c(350, 700),
    breaks = seq(350, 700, 100),
    expand = expansion(add = c(0, 0))
  ) +
  scale_x_datetime(
    expand = expansion(add = c(0, 1200)),
    date_breaks = "4 hours",
    date_labels = "%H:%M"
  ) +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(
    y = expression("CO"[2] * " (parts per million, ppm)")
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.key.width = unit(0.275, "cm"),
    legend.key.height = unit(0.2, "cm")
  )

save_plot(
  co2_pl,
  pdf_file = "results/data/co2-levels-over-time.png",
  w = 16, h = 18
)
```

### 2024-11-19 analysis/patient-tracking.Rmd
CO2 and occupancy time series plots

source("utils/plotting.r")
source("utils/spatial.r")
cellSize <- 250
source("preprocessing/prep_building-rasterize.R")
```

@@

```{r}
tracking_dates <- c(
  "2021-10-13", "2021-10-15", "2021-10-25", "2021-11-04", "2021-11-05"
)

@@

### Building

```{r}
cellSize <- 250
source("preprocessing/prep_building-rasterize.R")
```

@@

```{r}
track_count_time <- track_count_time %>%
  mutate(
    date = format(date, "%b %d"),
    date = factor(
      as.character(date),
      levels = c("Oct 13", "Oct 15", "Oct 25", "Nov 04", "Nov 05")
    ),
    time = as.POSIXct(format(date_time, format = "%H:%M:%S"), format = "%H:%M:%S")
  )

@@

save_plot(
  time_pl,
  pdf_file = "results/data/no-people-over-time.png",
  w = 8, h = 8
)
```

>>>>

source("utils/plotting.r")
source("utils/spatial.r")
source("preprocessing/prep_building-rasterize.R")
```

@@

```{r}
tracking_dates <- c(
  "2021-10-13", "2021-10-15", "2021-10-25", "2021-11-04", "2021-11-05"
)
abbr_dates <- format(as.Date(tracking_dates), format = "%b %d")

@@

@@

```{r}
track_count_time <- track_count_time %>%
  mutate(
    date = format(date, "%b %d"),
    date = factor(
      as.character(date),
      levels = c("Oct 13", "Oct 15", "Oct 25", "Nov 04", "Nov 05")
    ),
    time = as.POSIXct(format(
      date_time,
      format = "%H:%M:%S"
    ), format = "%H:%M:%S")
  )

@@

save_plot(
  time_pl,
  pdf_file = "results/data/no-people-over-time.png",
  w = 8, h = 8
)

time_by_day_pl <- track_count_time %>%
  mutate(
    time = as.POSIXct(
      format(date_time, format = "%H:%M:%S"),
      format = "%H:%M:%S"
    ),
    mthdy = factor(
      as.character(format(date, format = "%b %d")),
      levels = abbr_dates
    ),
    time = floor_date(time, "10 minutes")
  ) %>%
  group_by(mthdy, time, room) %>%
  summarize(n = mean(n)) %>%
  ungroup() %>%
  mutate(room = factor(
    room,
    levels = c("Waiting room", "Corridor", "TB room")
  )) %>%
  ggplot(aes(x = time, y = n, color = mthdy)) +
  geom_step() +
  facet_wrap(~room, ncol = 1) +
  scale_y_continuous(
    limits = c(0, NA),
    expand = expansion(add = c(0, 1))
  ) +
  scale_x_datetime(
    expand = expansion(add = c(0, 600)),
    date_breaks = "4 hours",
    date_labels = "%H:%M"
  ) +
  scale_color_manual(values = wes_palette("Moonrise3")) +
  labs(
    y = "Number of people"
  ) +
  theme_custom(8) +
  theme(
    axis.title.x = element_blank(),
    legend.title = element_blank(),
    legend.position = "bottom",
    legend.key.width = unit(0.275, "cm"),
    legend.key.height = unit(0.2, "cm")
  )

save_plot(
  time_by_day_pl,
  pdf_file = "results/data/no-people-over-time-by-day.png",
  w = 16, h = 18
)
```
